Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-05-14 table_fpp.tex

201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.6\times10^{-4}$ & $0.21$ & $5.6\times10^{-4}$ & Planet  \\
 \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $0.837$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.163$  & \color{red}  $0.20$  & \color{red}  $1.000$  & \color{red}  FP \\
201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.5\times10^{-3}$ & $0.21$ & $1.5\times10^{-3}$ & Planet  \\
201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.21$ & $1.8\times10^{-4}$ & Planet  \\
201367065.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.3\times10^{-4}$ & $0.22$ & $1.3\times10^{-4}$ & Planet\tablenotemark{c}  \\
201367065.02 & $0.67$ &  - & $3.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $3.8\times10^{-4}$ & Planet\tablenotemark{c}  \\
201384232.01 & $0.44$ &  - & $2.5\times10^{-3}$ & $3.9\times10^{-4}$ & $< 10^{-4}$ & $0.14$ & $2.9\times10^{-3}$ & Planet  \\
201393098.01 & $0.52$ &  - & $1.7\times10^{-4}$ & $< 10^{-4}$ & $8.5\times10^{-4}$ & $0.19$ & $1.0\times10^{-3}$ & Planet  \\
201403446.01 & $0.18$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
201445392.01 & $0.26$ &  - & $0.022$ & $2.8\times10^{-4}$ & $3.2\times10^{-3}$ & $0.19$ & $0.025$ & Candidate  \\
201445392.02 & $0.18$ &  - & $2.6\times10^{-3}$ & $< 10^{-4}$ & $0.048$ & $0.21$ & $0.051$ & Candidate  \\
201465501.01 & $0.68$ &  - & $< 10^{-4}$ & $0.152$ & $6.6\times10^{-3}$ & $0.20$ & $0.159$ & Candidate  \\
201505350.01 & $2.69$ &  - & $0.810$ & $< 10^{-4}$ & $0.018$ & $0.07$ & $0.828$ & Planet\tablenotemark{d}  \\
201505350.02 & $0.70$ &  - & $0.026$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $0.026$ & Planet\tablenotemark{d}  \\

@@

201549860.01 & $0.18$ &  - & $2.1\times10^{-4}$ & $< 10^{-4}$ & $2.2\times10^{-3}$ & $0.22$ & $2.4\times10^{-3}$ & Candidate\tablenotemark{a}  \\

@@

201565013.01 & $1.69$ &  - & $0.846$ & $9.3\times10^{-3}$ & $5.6\times10^{-3}$ & $0.07$ & $0.861$ & Candidate  \\
 \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.610$  & \color{red}  $0.383$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.993$  & \color{red}  FP \\
201577035.01 & $0.14$ &  Y & $7.0\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.08$ & $7.0\times10^{-3}$ & Planet  \\
201596316.01 & $0.45$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.8\times10^{-4}$ & $0.20$ & $3.8\times10^{-4}$ & Planet  \\
201613023.01 & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $< 10^{-4}$ & Planet  \\
201617985.01 & $0.27$ &  - & $1.9\times10^{-3}$ & $< 10^{-4}$ & $0.015$ & $0.20$ & $0.017$ & Candidate  \\
201629650.01 & $0.43$ &  - & $2.1\times10^{-3}$ & $< 10^{-4}$ & $1.6\times10^{-4}$ & $0.17$ & $2.3\times10^{-3}$ & Planet  \\
201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.3\times10^{-3}$ & $0.05$ & $5.3\times10^{-3}$ & Planet  \\
 \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.925$  & \color{red}  $0.072$  & \color{red}  $1.3\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.997$  & \color{red}  FP \\
201702477.01 & $0.70$ &  - & $0.343$ & $0.039$ & $1.3\times10^{-3}$ & $0.07$ & $0.384$ & Candidate  \\
201736247.01 & $0.42$ &  - & $9.2\times10^{-3}$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.17$ & $9.4\times10^{-3}$ & Planet  \\
201754305.01 & $0.65$ &  - & $1.1\times10^{-3}$ & $1.2\times10^{-4}$ & $1.5\times10^{-3}$ & $0.21$ & $2.7\times10^{-3}$ & Planet  \\
201754305.02 & $0.38$ &  - & $2.7\times10^{-3}$ & $< 10^{-4}$ & $7.5\times10^{-4}$ & $0.21$ & $3.5\times10^{-3}$ & Planet  \\
 \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.966$  & \color{red}  $0.022$  & \color{red}  $4.4\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.989$  & \color{red}  FP \\
201828749.01 & $0.39$ &  Y & $0.028$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $0.028$ & Candidate  \\
201855371.01 & $0.62$ &  - & $3.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $4.1\times10^{-4}$ & Planet  \\
201912552.01 & $0.47$ &  Y & $8.4\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $8.4\times10^{-4}$ & Planet  \\
 \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $0.240$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.020$  & \color{red}  $0.07$  & \color{red}  $0.260$  & \color{red}  FP\tablenotemark{b}  

>>>>

201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $8.0\times10^{-4}$ & $0.21$ & $8.0\times10^{-4}$ & Planet  \\
 \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $1.000$  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
201295312.01 & $0.04$ &  Y & $7.5\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $7.5\times10^{-4}$ & Candidate\tablenotemark{a}  \\
201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.2\times10^{-3}$ & $0.22$ & $2.2\times10^{-3}$ & Planet  \\
201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.6\times10^{-4}$ & $0.22$ & $1.6\times10^{-4}$ & Planet  \\
201367065.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-4}$ & $0.22$ & $2.0\times10^{-4}$ & Planet\tablenotemark{c}  \\
201367065.02 & $0.67$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Planet\tablenotemark{c}  \\
201384232.01 & $0.44$ &  - & $2.1\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.19$ & $2.2\times10^{-3}$ & Planet  \\
201393098.01 & $0.52$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $6.9\times10^{-4}$ & $0.21$ & $6.9\times10^{-4}$ & Planet  \\
201403446.01 & $0.18$ &  Y & $1.2\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $1.2\times10^{-3}$ & Candidate\tablenotemark{a}  \\
201445392.01 & $0.26$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.5\times10^{-3}$ & $0.20$ & $2.6\times10^{-3}$ & Planet  \\
201445392.02 & $0.18$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.032$ & $0.22$ & $0.032$ & Candidate  \\
201465501.01 & $0.68$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.4\times10^{-3}$ & $0.22$ & $5.4\times10^{-3}$ & Planet  \\
201505350.01 & $2.69$ &  - & $8.5\times10^{-3}$ & $< 10^{-4}$ & $2.5\times10^{-3}$ & $0.09$ & $0.011$ & Planet\tablenotemark{d}  \\
201505350.02 & $0.70$ &  - & $1.6\times10^{-3}$ & $< 10^{-4}$ & $4.8\times10^{-4}$ & $0.05$ & $2.1\times10^{-3}$ & Planet\tablenotemark{d}  \\

@@

201549860.01 & $0.18$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-3}$ & $0.21$ & $2.0\times10^{-3}$ & Candidate\tablenotemark{a}  \\

@@

201565013.01 & $1.69$ &  - & $0.802$ & $0.058$ & $5.9\times10^{-3}$ & $0.07$ & $0.866$ & Candidate  \\
 \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.668$  & \color{red}  $0.332$  & \color{red}  $2.4\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
201577035.01 & $0.14$ &  Y & $7.5\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.10$ & $7.6\times10^{-4}$ & Planet  \\
201596316.01 & $0.45$ &  - & $1.0\times10^{-3}$ & $< 10^{-4}$ & $5.9\times10^{-3}$ & $0.07$ & $6.9\times10^{-3}$ & Planet  \\
201613023.01 & $0.08$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.22$ & $< 10^{-4}$ & Planet  \\
201617985.01 & $0.27$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.013$ & $0.18$ & $0.013$ & Candidate  \\
201629650.01 & $0.43$ &  - & $1.1\times10^{-3}$ & $< 10^{-4}$ & $3.4\times10^{-4}$ & $0.21$ & $1.4\times10^{-3}$ & Planet  \\
201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.5\times10^{-3}$ & $0.05$ & $4.5\times10^{-3}$ & Planet  \\
 \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.924$  & \color{red}  $0.076$  & \color{red}  $1.0\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP \\
201702477.01 & $0.70$ &  - & $0.150$ & $2.4\times10^{-3}$ & $2.4\times10^{-3}$ & $0.06$ & $0.155$ & Candidate  \\
201736247.01 & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.19$ & $2.7\times10^{-4}$ & Planet  \\
201754305.01 & $0.65$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.4\times10^{-3}$ & $0.22$ & $1.4\times10^{-3}$ & Planet  \\
201754305.02 & $0.38$ &  - & $1.1\times10^{-4}$ & $< 10^{-4}$ & $7.8\times10^{-4}$ & $0.22$ & $8.9\times10^{-4}$ & Planet  \\
 \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.980$  & \color{red}  $2.5\times10^{-3}$  & \color{red}  $7.3\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.984$  & \color{red}  FP \\
201828749.01 & $0.39$ &  Y & $0.242$ & $< 10^{-4}$ & $1.5\times10^{-3}$ & $0.07$ & $0.244$ & Candidate  \\
 \color{red} 201855371.01  & \color{red}  $0.62$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.925$  & \color{red}  $0.01$  & \color{red}  $0.925$  & \color{red}  FP \\
201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet  \\
 \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.000$  & \color{red}  $0.00$  & \color{red}  $1.000$  & \color{red}  FP\tablenotemark{b}  
